---
title: "yearly_injuries_cleanup"
output: html_document
date: "2026-02-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

yearly_injuries manual cleanup
- removing extra headers and footnotes
- deleting extra space between each year
- remove participant column and percent concussion related column (because not all years have these columns)
- shifted all columns to fill gaps from deleted columns
- added year column
- removing column titles between years
- deleted parentheses/negative signs randomly found in data values
- go in and reformat percent column because only the first row has % symbol
- changed all of the percents into actual numbers, since half the data set is in numbers and half is in percent
  - we did this by adding columns in the data for years 2007-2014
  - replaced all the percent columns by these added columns

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
